True versus apparent shapes of astrophysical bow shocks

### 2017-03-28 papers/Paper1/sec-quadrics-observations.tex
Add 1 and 2 star sources to R0-R0 graph

\bigskip
Only sources with a 3-star or higher rating are used in the following analysis, which amount to approximately half (227 out of 471) of all the MIPSGAL arc sources.

>>>>

\bigskip
Only sources with a 3-star or higher rating are used in the following analysis, which comprise approximately half (227 out of 471) of all the MIPSGAL arc sources.  In some cases of poor and failed fits, there is nothing apparently ``wrong'' with the source itself, and it is likely that minor tweaks to the methodology would improve matters.  But we have elected not to do so, in order to maintain a uniform methodology across all sources.

Figure~\ref{fig:mipsgal-examples}d compares the bow shock size,
\(R_0\), determined by our fits (vertical axis) with the corresponding
value given in the \citet{Kobulnicky:2016a} catalog (horizontal axis).
For most sources with 3-star or higher rating, the two estimates agree
to within \(\pm 20\%\), but there are a small number of sources with a
discrepancy of more than a factor of two.  In all cases that we
checked, we believe that our estimates of \(R_0\) are more accurate
than those in the catalog.
